~\Large Increased sexual dimorphism evolves in a fossil stickleback following ecological release from fish piscivores

### 2024-09-18 manuscript/paper.tex
some manuscript work

\title{~\Large Increased sexual dimorphism evolves in a fossil
stickleback following ecological release from fish piscivores}
\author{\large Allison Ozark\(^{1,*}\), Matthew Stuart\(^{2,3,*}\),
Raheyma Siddiqui\(^1\), Akhil Ghosh\(^{2,3}\)\\
\large Samantha Swank\(^1\), Michael A. Bell\(^4\), Gregory J.
Matthews\(^{2,3}\), and Yoel E. Stuart\(^{1,+}\)\\
\vspace{-1.1mm}\\
\large \(^1\) Department of Biology, Loyola University Chicago, Chicago,
IL, USA \vspace{-1.1mm}\\
\large \(^2\) Department of Mathematics and Statistics, Loyola
University Chicago, Chicago, IL, USA \vspace{-1.1mm}\\
\large \(^3\) Center for Data Science and Consulting, Loyola University
Chicago, Chicago, IL, USA \vspace{-1.1mm}\\
\large \(^4\) University of California Museum of Paleontology, Berkeley,
CA, USA \vspace{-1.1mm}\\
\large \(^*\) Equal contribution \vspace{-1.1mm}\\
\large \(^+\) Corresponding:
\href{mailto:ystuart@luc.edu}{\nolinkurl{ystuart@luc.edu}}
\vspace{-1.1mm}}
\date{}

>>>>

\title{~\Large Increased sexual dimorphism evolves in a fossil
stickleback following ecological release from fish piscivores}
\author{\large Matthew Stuart\(^{1,2}\), Allison Ozark\(^{3}\), Raheyma
Siddiqui\(^3\), Akhil Ghosh\(^{1,2}\)\\
\large Samantha Swank\(^3\), Michael A. Bell\(^4\), Gregory J.
Matthews\(^{1,2}\), and Yoel E. Stuart\(^{3,+}\)\\
\vspace{-1.1mm}\\
\large \(^1\) Department of Mathematics and Statistics, Loyola
University Chicago, Chicago, IL, USA \vspace{-1.1mm}\\
\large \(^2\) Center for Data Science and Consulting, Loyola University
Chicago, Chicago, IL, USA \vspace{-1.1mm}\\
\large \(^3\) Department of Biology, Loyola University Chicago, Chicago,
IL, USA \vspace{-1.1mm}\\
\large \(^4\) University of California Museum of Paleontology, Berkeley,
CA, USA \vspace{-1.1mm}\\
\large \(^+\) Corresponding:
\href{mailto:ystuart@luc.edu}{\nolinkurl{ystuart@luc.edu}}
\vspace{-1.1mm}}
\date{}
